Impact of the 2016 Presidential Election on Urban Mobility: Who is Affected the Most?

### 2019-12-09 manuscript.Rmd
Clean up code

```{r dist_to_center}
# Compute distance from Washington Monument
mnm <- tribble(
  ~latitude, ~longitude,
  38.8895, -77.0353
)

@@

#Averaged travel times over weeks 1 and 2 in January
weeks12 <- travel_time_sf %>%
  filter(year %in% 2017) %>%
  filter(month %in% 1) %>%
  filter(week %in% 1:2) %>%
  select(GEOID,mean_travel_time) %>%
  as.data.frame() %>%
  group_by(GEOID) %>%
  summarize(MeanTimeNorm = mean(mean_travel_time))

#Averaged travel times over weeks 3 and 4 in January
weeks34 <- travel_time_sf %>%
  filter(year %in% 2017) %>%
  filter(month %in% 1) %>%
  filter(week %in% 3:4) %>%
  select(GEOID,mean_travel_time) %>%
  as.data.frame() %>%
  group_by(GEOID) %>%
  summarize(MeanTimeIng = mean(mean_travel_time))

mod1data <- travel_time_sf %>%
  filter(year %in% 2017) %>%
  filter(month %in% 1) %>%
  filter(week %in% c(1:2)) %>%
  dplyr::select(GEOID, starts_with('med_'),starts_with('white'),starts_with('asian'),starts_with('black'),starts_with('car_trans'),starts_with('public_trans'),NumRoads,NumMetro, distance) %>%
  distinct(GEOID) %>%
  left_join(weeks12)

mod2data <- travel_time_sf %>%
  filter(year %in% 2017) %>%
  filter(month %in% 1) %>%
  filter(week %in% c(3:4)) %>%
  dplyr::select(GEOID, starts_with('med_'),starts_with('white'),starts_with('asian'),starts_with('black'),starts_with('car_trans'),starts_with('public_trans'),NumRoads,NumMetro, distance) %>%
  distinct(GEOID) %>%
  left_join(weeks34)

weeksdiff = left_join(weeks12,weeks34) %>%
  mutate(diffMeanTime = MeanTimeIng-MeanTimeNorm)

mod3data <- travel_time_sf %>%
  filter(year %in% 2017) %>%
  filter(month %in% 1) %>%
  filter(week %in% 1) %>%
  dplyr::select(GEOID, med_incomeE, med_incomeM, asianE, asianM, blackE, blackM, public_transitE, public_transitM, car_transitE, car_transitM, NumRoads, NumMetro, distance) %>%
  left_join(weeksdiff)
```

```{r}
head(mod1data)
```

Normal mean time model

@@

```{r}
Queen <- as.nb.sgbp(st_queen(mod1data))
W <- nb2mat(Queen, style='B', zero.policy = TRUE)

```

```{r CSR_test}
listW = nb2listw(Queen)
dc_sar = spautolm(formula = MeanTimeNorm ~ med_incomeE + med_incomeM + asianE + asianM + blackE + blackM + public_transitE + public_transitM + car_transitE + car_transitM + NumRoads + NumMetro+distance, data = mod1data, listw = listW, family = "SAR")

summary(dc_sar)
```

```{r CSR_test}
listW = nb2listw(Queen)
dc_sar2 = spautolm(formula = MeanTimeNorm ~ NumRoads+NumMetro+distance, data = mod1data, listw = listW, family = "SAR")

summary(dc_sar2)

Queen <- as.nb.sgbp(st_queen(weeks34))
W <- nb2mat(Queen, style='B', zero.policy = TRUE)

plot(weeks34["mean_travel_time"])
plot(Queen, weekw34$centroids, col="blue", cex = 0.5, lwd = 0.5)
```

```{r CSR_test}
listW = nb2listw(Queen)
dc_sar2 = spautolm(formula = MeanTimeNorm ~ med_incomeE + asianE + blackE + public_transitE + NumRoads + NumMetro+distance, data = mod1data, listw = listW, family = "SAR")

summary(dc_sar2)
```

@@

```{r}
QueenDiff <- as.nb.sgbp(st_queen(mod3data))
W <- nb2mat(Queen, style='B', zero.policy = TRUE)

```

```{r}
listW = nb2listw(QueenDiff)
dc_sar_diff = spautolm(formula = MeanTimeNorm ~ med_incomeE + asianE + blackE + public_transitE + NumRoads + NumMetro+distance, data = mod3data, listw = listW, family = "SAR")

@@

```{r}
Moran.I(week_1$mean_travel_time, W, na.rm=TRUE)
```

>>>>

```{r dist_to_center march_inaug}
# Compute distance from Washington Monument
mnm <- tribble(
  ~latitude, ~longitude,
  38.8895, -77.0353
)

@@

# Average travel times over weeks 1 and 2 in January (before inauguration)
weeks12 <- travel_time_sf %>%
  filter(year %in% 2017) %>%
  filter(month %in% 1) %>%
  filter(week %in% 1:2) %>%
  select(GEOID,mean_travel_time) %>%
  as.data.frame() %>%
  group_by(GEOID) %>%
  summarize(MeanTimeNorm = mean(mean_travel_time))

weeks12_data <- travel_time_sf %>%
  filter(year %in% 2017) %>%
  filter(month %in% 1) %>%
  filter(week %in% c(1:2)) %>%
  distinct(GEOID, .keep_all = TRUE) %>%
  dplyr::select(GEOID, starts_with('med_'), starts_with('white'), starts_with('asian'), starts_with('black'), starts_with('car_trans'), starts_with('public_trans'), NumRoads, NumMetro, distance) %>%
  left_join(weeks12, by = 'GEOID')

# Average travel times over weeks 3 and 4 in January (during & after inauguration)
weeks34 <- travel_time_sf %>%
  filter(year %in% 2017) %>%
  filter(month %in% 1) %>%
  filter(week %in% 3:4) %>%
  select(GEOID,mean_travel_time) %>%
  as.data.frame() %>%
  group_by(GEOID) %>%
  summarize(MeanTimeIng = mean(mean_travel_time))

weeks34_data <- travel_time_sf %>%
  filter(year %in% 2017) %>%
  filter(month %in% 1) %>%
  filter(week %in% c(3:4)) %>%
  distinct(GEOID, .keep_all = TRUE) %>%
  dplyr::select(GEOID, starts_with('med_'), starts_with('white'), starts_with('asian'), starts_with('black'), starts_with('car_trans'), starts_with('public_trans'), NumRoads, NumMetro, distance) %>%
  left_join(weeks34, by = 'GEOID')

# Take difference in average travel times before and after inauguration
weeksdiff <- left_join(weeks12, weeks34) %>%
  mutate(diffMeanTime = MeanTimeIng - MeanTimeNorm)

weeksdiff_data <- travel_time_sf %>%
  filter(year %in% 2017) %>%
  filter(month %in% 1) %>%
  filter(week %in% 1) %>%
  dplyr::select(GEOID, med_incomeE, med_incomeM, asianE, asianM, blackE, blackM, public_transitE, public_transitM, car_transitE, car_transitM, NumRoads, NumMetro, distance) %>%
  left_join(weeksdiff, by = 'GEOID')
```

Normal Mean Time Model

@@

```{r}
queen12 <- as.nb.sgbp(st_queen(weeks12_data))
W <- nb2mat(queen12, style='B', zero.policy = TRUE)
listW <- nb2listw(queen12)

dc_sar_12 <- spautolm(formula = MeanTimeNorm ~ med_incomeE + med_incomeM + asianE + asianM + blackE + blackM + public_transitE + public_transitM + car_transitE + car_transitM + NumRoads + NumMetro + distance, data = weeks12_data, listw = listW, family = "SAR")

summary(dc_sar_12)
# plot(weeks12["mean_travel_time"])
# plot(queen12, weeks12$centroids, col="blue", cex = 0.5, lwd = 0.5)
```

```{r CSR_test}
queen34 <- as.nb.sgbp(st_queen(weeks34_data))
W <- nb2mat(queen34, style='B', zero.policy = TRUE)
listW <- nb2listw(queen34)

dc_sar_34 <- spautolm(formula = MeanTimeIng ~ med_incomeE + med_incomeM + asianE + asianM + blackE + blackM + public_transitE + public_transitM + car_transitE + car_transitM + NumRoads + NumMetro + distance, data = weeks34_data, listw = listW, family = "SAR")

summary(dc_sar_34)
# plot(weeks34["mean_travel_time"])
# plot(queen34, weeks34$centroids, col="blue", cex = 0.5, lwd = 0.5)
```

@@

```{r}
queen_diff <- as.nb.sgbp(st_queen(weeksdiff_data))
W <- nb2mat(queen_diff, style='B', zero.policy = TRUE)
listW <- nb2listw(queen_diff)

dc_sar_diff <- spautolm(formula = diffMeanTime ~ med_incomeE + med_incomeM + asianE + asianM + blackE + blackM + public_transitE + public_transitM + car_transitE + car_transitM + NumRoads + NumMetro + distance, data = weeksdiff_data, listw = listW, family = "SAR")

@@
